---
title: "Experiments 53-55"
author: "Erik J Peterson"
date: "8-26-2015"
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
---


# Background was stim; PAC works by assembly recruitment.

N = 500

```{r helper_fns, echo=FALSE, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(gridExtra)

path <- "/home/ejp/src/pacological/data"

load.data <- function(path, type, rates){
  df <- NULL
  for(r_o in rates){
    for(r_s in rates){
      try({
        name <- paste("Iosc-", as.character(r_o), 
                      "_Istim-", as.character(r_s), 
                      "_", as.character(type), 
                      "_summary.csv", sep="")
        di <- read.csv(paste(path, name, sep=""))
        di["Iosc"] <- rep(r_o, nrow(di))
        di["Istim"] <- rep(r_s, nrow(di))
        
        df <- rbind(df, di)  
        })
      }
    }
  df
  }
```

```{r exps, echo=FALSE, warning=FALSE, message=FALSE}
rates <- c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30)

exp53path <- paste(path, "/exp53/", sep="")
mi_exp53 <- load.data(exp53path, "MI", rates)
h_exp53 <- load.data(exp53path, "H", rates)
pac_exp53 <- load.data(exp53path, "PAC", rates)

exp54path <- paste(path, "/exp54/", sep="")
mi_exp54 <- load.data(exp54path, "MI", rates)
h_exp54 <- load.data(exp54path, "H", rates)
pac_exp54 <- load.data(exp54path, "PAC", rates)

exp55path <- paste(path, "/exp55/", sep="")
mi_exp55 <- load.data(exp55path, "MI", rates)
h_exp55 <- load.data(exp55path, "H", rates)
pac_exp55 <- load.data(exp55path, "PAC", rates)
```

## MIs

### Gain
```{r plot_mi_gain, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim53 <- stat_summary(data=subset(mi_exp53, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p53 <- ggplot(data=subset(mi_exp53, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim53 + theme_bw() + ggtitle("exp53\np_n = 0.25") + ylim(0,2)

stim54 <- stat_summary(data=subset(mi_exp54, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p54 <- ggplot(data=subset(mi_exp54, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim54 + theme_bw() + ggtitle("exp54\np_n = 0.5") + ylim(0,2)

stim55 <- stat_summary(data=subset(mi_exp55, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p55 <- ggplot(data=subset(mi_exp55, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim55 + theme_bw() + ggtitle("exp55\np_n = 0.75") + ylim(0,2)

grid.arrange(p53, p54, p55, nrow=1)
```

* Increasing recruitment (i.e. `p_n`) increases MI. If `p_n` becomes one (at N=250) I(PAC,S) would be beneficial
* Overall neuron number still crucial in setting beneficial versus patological PAC

### Additive

```{r plot_mi_add, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim53 <- stat_summary(data=subset(mi_exp53, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p53 <- ggplot(data=subset(mi_exp53, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim53 + theme_bw() + ggtitle("exp53\np_n = 0.25") + ylim(0,2)

stim54 <- stat_summary(data=subset(mi_exp54, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p54 <- ggplot(data=subset(mi_exp54, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim54 + theme_bw() + ggtitle("exp54\np_n = 0.5") + ylim(0,2)

stim55 <- stat_summary(data=subset(mi_exp55, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p55 <- ggplot(data=subset(mi_exp55, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim55 + theme_bw() + ggtitle("exp55\np_n = 0.75") + ylim(0,2)

grid.arrange(p53, p54, p55, nrow=1)
```

* Recruiment has no effect. PAC is always pathological.

### Subtractive

```{r plot_mi_sub, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim53 <- stat_summary(data=subset(mi_exp53, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p53 <- ggplot(data=subset(mi_exp53, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim53 + theme_bw() + ggtitle("exp53\np_n = 0.25") + ylim(0,2)

stim54 <- stat_summary(data=subset(mi_exp54, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p54 <- ggplot(data=subset(mi_exp54, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim54 + theme_bw() + ggtitle("exp54\np_n = 0.5") + ylim(0,2)

stim55 <- stat_summary(data=subset(mi_exp55, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p55 <- ggplot(data=subset(mi_exp55, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim55 + theme_bw() + ggtitle("exp55\np_n = 0.75") + ylim(0,2)

grid.arrange(p53, p54, p55, nrow=1)
```

* At low `p_n` subtraction *enhances* MI. (Very unexpected.)
* Recruiment inversely related to enhancement, but
* Even strong recruitment gives nearly beneficial PAC

## PACs

```{r plot_pac, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim53 <- stat_summary(data=subset(pac_exp53, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p53 <- ggplot(data=subset(pac_exp53, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim53 + theme_bw() + ggtitle("exp53\np_n = 0.25") + ylim(0,1)

stim54 <- stat_summary(data=subset(pac_exp54, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p54 <- ggplot(data=subset(pac_exp54, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim54 + theme_bw() + ggtitle("exp54\np_n = 0.5") + ylim(0,1)

stim55 <- stat_summary(data=subset(pac_exp55, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p55 <- ggplot(data=subset(pac_exp55, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim55 + theme_bw() + ggtitle("exp55\np_n = 0.75") + ylim(0,1)

grid.arrange(p53, p54, p55, nrow=1)
```

