---
title: "Phase-amplitude coupling, neural computation, and information transmission: results"
author: "Erik Peterson"
date: "June 18, 2015"
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(gridExtra)

path <- "/home/ejp/src/pacological/data"
exp1path <- paste(path, "/exp1/", sep="")

rates <- c(2, 6, 10, 14, 18, 22, 26, 30, 34, 38, 42, 46, 50, 54, 58)

mi_exp1 <- NULL
for(r_o in rates){
  for(r_s in rates){
    try({
      name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                    as.character(r_s), "_MI_summary.csv", sep="")
      di <- read.csv(paste(exp1path, name, sep=""))
      di["Iosc"] <- rep(r_o, nrow(di))
      di["Istim"] <- rep(r_s, nrow(di))
      mi_exp1 <- rbind(mi_exp1, di)  
    }) 
  }
}

h_exp1 <- NULL
for(r_o in rates){
  for(r_s in rates){
    try({
      name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                    as.character(r_s), "_H_summary.csv", sep="")
      di <- read.csv(paste(exp1path, name, sep=""))
      di["Iosc"] <- rep(r_o, nrow(di))
      di["Istim"] <- rep(r_s, nrow(di))
      h_exp1 <- rbind(h_exp1, di)  
    }) 
  }
}

pac_exp1 <- NULL
for(r_o in rates){
  for(r_s in rates){
    try({
      name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                    as.character(r_s), "_PAC_summary.csv", sep="")
      di <- read.csv(paste(exp1path, name, sep=""))
      di["Iosc"] <- rep(r_o, nrow(di))
      di["Istim"] <- rep(r_s, nrow(di))
      pac_exp1 <- rbind(pac_exp1, di)  
    }) 
  }
}
```

# Rate (Poisson) coding

## Gain (multiplicative) interactions

First we look at the relation between Istim and {MI, H, PAC}, as a function of Iosc magnitude (blue). Metrics for stimulus-only are included for comparison (red).

```{r, echo=FALSE, fig.width=4, fig.height=8}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("gain_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("MI") + stat_summary(data=mi_exp1[mi_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p2 <- qplot(data=h_exp1[h_exp1$X %in% c("gain_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("H") + stat_summary(data=h_exp1[h_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p3 <- qplot(data=pac_exp1[pac_exp1$X %in% c("gain_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("Istim") + ylab("PAC") + stat_summary(data=pac_exp1[pac_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

grid.arrange(p1, p2, p3, ncol=1)
```

To better see the Istim/Iosc relation, replot as a heatmap. These do not correct for stimulus-only. (Should change that in the future?)

```{r, echo=FALSE, fig.width=4, fig.height=9}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("gain_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("MI")

p2 <- qplot(data=h_exp1[h_exp1$X %in% c("gain_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("H")

p3 <- qplot(data=pac_exp1[pac_exp1$X %in% c("gain_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("PAC")

grid.arrange(p1, p2, p3, ncol=1)
```

* For Istim below 20 Hz, gain improves MI.
* Effect is quite pronounces for low stimulus firing rates (2 Hz),
* the rapidly declines and recovers, eventually plateauing at or near stimulus MI.
* H increases with gain and Iosc, but the Iosc effect diminishes as Istim and Iosc approach each other.
* Once Iosc hits 10 Hz there is a strong non-linear decline and rise in PAC as a function of Istim. This negative peak shifts leftward as Iosc increases. Curious


### Are MI, H and PAC correlated?

For all data....

```{r}
cor.test(mi_exp1[mi_exp1$X %in% c("gain_p"),]$mean, h_exp1[h_exp1$X %in% c("gain_p"),]$mean)
cor.test(mi_exp1[mi_exp1$X %in% c("gain_p"),]$mean, pac_exp1[pac_exp1$X %in% c("gain_p"),]$mean)
cor.test(h_exp1[h_exp1$X %in% c("gain_p"),]$mean, pac_exp1[pac_exp1$X %in% c("gain_p"),]$mean)
```

* Yes.
* Negatively in the case of (MI, PAC) and (H, PAC)
* Positively in the case of (H, and MI)

## Additive interactions

Plots structure same as for above.


```{r, echo=FALSE, fig.width=4, fig.height=8}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("summed_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("MI") + stat_summary(data=mi_exp1[mi_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p2 <- qplot(data=h_exp1[h_exp1$X %in% c("summed_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("H") + stat_summary(data=h_exp1[h_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p3 <- qplot(data=pac_exp1[pac_exp1$X %in% c("summed_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("Istim") + ylab("PAC") + stat_summary(data=pac_exp1[pac_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

grid.arrange(p1, p2, p3, ncol=1)
# p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("summed_p", "stim_p"),], x=Istim, color=X, y=mean, geom="line", facets=.~Iosc) + theme_bw() + xlim(1,60) + xlab("") + ylab("MI")
# 
# p2 <- qplot(data=h_exp1[mi_exp1$X %in% c("summed_p", "stim_p"),], x=Istim, color=X, y=mean, geom="line", facets=.~Iosc) + theme_bw() + xlim(1,60) + xlab("") + ylab("H")
# 
# p3 <- qplot(data=pac_exp1[mi_exp1$X %in% c("summed_p", "stim_p"),], x=Istim, color=X, y=mean, geom="line", facets=.~Iosc) + theme_bw() + xlim(1,60) + xlab("Istim") + ylab("PAC")
```

```{r, echo=FALSE, fig.width=4, fig.height=8}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("summed_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("MI")

p2 <- qplot(data=h_exp1[h_exp1$X %in% c("summed_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("H")

p3 <- qplot(data=pac_exp1[pac_exp1$X %in% c("summed_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("PAC")

grid.arrange(p1, p2, p3, ncol=1)
```

* Additive has no effect on MI,
* but does increase H 
* and reliably increases PAC.
* The stronger the stimulus, the less PAC. Stronger Ioscs only mitigate somewhat the decline.


## Subtractive interaction

Plot structure identical to silenced (above).

```{r, echo=FALSE, fig.width=4, fig.height=8}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("silenced_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("MI") + stat_summary(data=mi_exp1[mi_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p2 <- qplot(data=h_exp1[h_exp1$X %in% c("silenced_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("H") + stat_summary(data=h_exp1[h_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p3 <- qplot(data=pac_exp1[pac_exp1$X %in% c("silenced_p"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("Istim") + ylab("PAC") + stat_summary(data=pac_exp1[pac_exp1$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

grid.arrange(p1, p2, p3, ncol=1)
```

```{r, warning=FALSE, echo=FALSE, fig.width=4, fig.height=8}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("silenced_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("MI")

p2 <- qplot(data=h_exp1[h_exp1$X %in% c("silenced_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("H")

p3 <- qplot(data=pac_exp1[pac_exp1$X %in% c("silenced_p"),], x=Istim, y=Iosc, fill=mean, geom="tile") + theme_minimal() + ggtitle("PAC")

grid.arrange(p1, p2, p3, ncol=1)
```

* Subtraction has sub-stimulus H and MI,
* but strong and consistent robust PAC. As with the additive interaction, PAC declines wit Istim, 
* but in this case increasing Iosc completely mitigates the effect.

# Binary (synchrony) coding

## Stimulus encoding quality between Poisson and Binary codes.

(An initial quick, dirty, comparison)

First we just compare their respective stimulus encoding. K (network synchrony) was fixed for the binary sample.


```{r, warning=FALSE, echo=FALSE, fig.width=11, fig.height=4}
p1 <- qplot(data=mi_exp1[mi_exp1$X %in% c("stim_b", "stim_p"),], x=Istim, color=X, y=mean, geom="line", facets=.~Iosc) + theme_bw() + xlim(1,60) + xlab("") + ylab("MI")

p2 <- qplot(data=h_exp1[mi_exp1$X %in% c("stim_b", "stim_p"),], x=Istim, color=X, y=mean, geom="line", facets=.~Iosc) + theme_bw() + xlim(1,60) + xlab("Istim") + ylab("H")
grid.arrange(p1, p2, ncol=1)
```

* MI and H higher for Poisson coding,
* but the `excitability` of the binary model was very low (excitability = 0.00001). See Exp 4?

## Increasing synchrony (k)

Driving rate was held constant, as was excitability, while k was increased.  Two fixed rates were examined, a high (30 Hz) and a low (2 Hz). These analyses focus on the gain (multiplicative) interaction only. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
exp2path <- paste(path, "/exp2/", sep="")

ks <- c(1, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
rates <- c(2, 30)

mi_exp2 <- NULL
for(k in ks){
  try({
    name <- paste("Iosc-", as.character(rates[1]), "_Istim-", 
                  as.character(rates[2]), "_k-", as.character(k),
                  "_MI_summary.csv", sep="")
    di <- read.csv(paste(exp2path, name, sep=""))
    di["ks"] <- rep(k, nrow(di))
    mi_exp2 <- rbind(mi_exp2, di)  
    }) 
}

h_exp2 <- NULL
for(k in ks){
  try({
    name <- paste("Iosc-", as.character(rates[1]), "_Istim-", 
                  as.character(rates[2]), "_k-", as.character(k),
                  "_H_summary.csv", sep="")
    di <- read.csv(paste(exp2path, name, sep=""))
    di["ks"] <- rep(k, nrow(di))
    h_exp2 <- rbind(h_exp2, di)  
    }) 
}

pac_exp2 <- NULL
for(k in ks){
  try({
    name <- paste("Iosc-", as.character(rates[1]), "_Istim-", 
                  as.character(rates[2]), "_k-", as.character(k),
                  "_PAC_summary.csv", sep="")
    di <- read.csv(paste(exp2path, name, sep=""))
    di["ks"] <- rep(k, nrow(di))
    pac_exp2 <- rbind(pac_exp2, di)  
    }) 
}
```

### Compare increasing synchrony (k) to fixed Poisson rate.

```{r, echo=FALSE, warning=FALSE, fig.width=3, fig.height=4}
p1 <- qplot(data=mi_exp2[mi_exp2$X %in% c("stim_b", "stim_p"),], x=ks, color=X, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("k") + ylab("MI")

p2 <- qplot(data=h_exp2[h_exp2$X %in% c("stim_b", "stim_p"),], x=ks, color=X, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("k") + ylab("H")

grid.arrange(p1, p2, ncol=1)
```

* For rates below 20 Hz, Poisson provides higher MI. 
* By 20 Hz the two codes are equivalent. 
* In all cases Poisson coding has higher H.

### High stimulus rate, low oscillation rate

```{r, echo=FALSE, warning=FALSE, fig.width=3, fig.height=5}
p1 <- qplot(data=mi_exp2[mi_exp2$X %in% c("gain_b", "stim_b"),], x=ks, color=X, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("MI")

p2 <- qplot(data=h_exp2[h_exp2$X %in% c("gain_b", "stim_b"),], x=ks, color=X, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("") + ylab("H")

p3 <- qplot(data=pac_exp2[pac_exp2$X %in% c("gain_b", "stim_b"),], x=ks, color=X, y=mean, geom="line") + theme_bw() + xlim(1,60) + xlab("k") + ylab("PAC")

grid.arrange(p1, p2, p3, ncol=1)
```

* Low stimulus has worse MI and H than Poisson (not shown).
* Low k (below 10) improves MI over stimulus, followed by a plateau.
* As K increases so does H in both stimulus and gain, while
* gain is larger overall.

### Increasing synchrony and excitability.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
exp4path <- paste(path, "/exp4/", sep="")

ks <- c(1, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
excites <- c("0.001", "0.005", "0.0001", "0.0005", "0.00001")

mi_exp4 <- NULL
for(k in ks){
  for(ex in excites){
    try({
      name <- paste("k-", k, "_ex-", as.character(ex),
                    "_MI_summary.csv", sep="")
      di <- read.csv(paste(exp4path, name, sep=""))
      di["ks"] <- rep(k, nrow(di))
      di["excitability"] <- rep(ex, nrow(di))
      mi_exp4 <- rbind(mi_exp4, di)  
      })   
  }
}
```

```{r, echo=FALSE, warning=FALSE, fig.width=8, fig.height=3}
qplot(data=mi_exp4[mi_exp4$X %in% c("stim_b", "stim_p"),], x=ks, color=X, y=mean, geom="line", facets=.~excitability) + theme_bw() + xlim(1,60) + xlab("k") + ylab("MI")

# grid.arrange(p1, p2, ncol=1)
```

TODO - look a rates

# Bernoulli (synchrony) coding

```{r, echo=FALSE, warning=FALSE, message=FALSE}
exp5path <- paste(path, "/exp5/", sep="")

rates = c(5, 10, 15, 20, 25, 30)
excites = c("0.2", "0.1", "0.05")

mi_exp5 <- NULL
for(r_o in rates){
  for(r_s in rates){
    for(ex in excites){
      try({
        name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                      as.character(r_s), "_ex-", ex, "_MI_summary.csv", sep="")
        di <- read.csv(paste(exp5path, name, sep=""))
        di["Iosc"] <- rep(r_o, nrow(di))
        di["Istim"] <- rep(r_s, nrow(di))
        di["excitability"] <- rep(ex, nrow(di))
        mi_exp5 <- rbind(mi_exp5, di)  
        })   
    }
  }
}

h_exp5 <- NULL
for(r_o in rates){
  for(r_s in rates){
    for(ex in excites){
      try({
        name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                      as.character(r_s), "_ex-", ex, "_H_summary.csv", sep="")
        di <- read.csv(paste(exp5path, name, sep=""))
        di["Iosc"] <- rep(r_o, nrow(di))
        di["Istim"] <- rep(r_s, nrow(di))
        di["excitability"] <- rep(ex, nrow(di))
        h_exp5 <- rbind(h_exp5, di)  
        })   
    }
  }
}

pac_exp5 <- NULL
for(r_o in rates){
  for(r_s in rates){
    for(ex in excites){
      try({
        name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                      as.character(r_s), "_ex-", ex, "_PAC_summary.csv", sep="")
        di <- read.csv(paste(exp5path, name, sep=""))
        di["Iosc"] <- rep(r_o, nrow(di))
        di["Istim"] <- rep(r_s, nrow(di))
        di["excitability"] <- rep(ex, nrow(di))
        pac_exp5 <- rbind(pac_exp5, di)  
        })   
    }
  }
}

rate_exp5 <- NULL
for(r_o in rates){
  for(r_s in rates){
    for(ex in excites){
      try({
        name <- paste("Iosc-", as.character(r_o), "_Istim-", 
                      as.character(r_s), "_ex-", ex, "_rate_summary.csv", sep="")
        di <- read.csv(paste(exp5path, name, sep=""))
        di["Iosc"] <- rep(r_o, nrow(di))
        di["Istim"] <- rep(r_s, nrow(di))
        di["excitability"] <- rep(ex, nrow(di))
        rate_exp5 <- rbind(rate_exp5, di)  
        })   
    }
  }
}
```

```{r, echo=FALSE, fig.width=6, fig.height=7}
p1 <- qplot(data=mi_exp5[mi_exp5$X %in% c("gain_b"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line", facets=.~excitability) + theme_bw()  + xlab("") + ylab("MI") + stat_summary(data=mi_exp5[mi_exp5$X %in% c("stim_b"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p2 <- qplot(data=h_exp5[h_exp5$X %in% c("gain_b"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line", facets=.~excitability) + theme_bw() + xlab("") + ylab("H") + stat_summary(data=h_exp5[h_exp5$X %in% c("stim_b"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

p3 <- qplot(data=pac_exp5[pac_exp5$X %in% c("gain_b"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line", facets=.~excitability) + theme_bw() + xlim(1,60) + xlab("Istim") + ylab("PAC") + stat_summary(data=pac_exp5[pac_exp5$X %in% c("stim_b"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
grid.arrange(p1, p2, p3, ncol=1)
```

# Oscillations induce a transition to syhchronous firing.

Stimulus firing is baseline poissonic, but the oscillation's phase induces a transition to synchronous firing.

## Bernoulli

Model synchronous firing using the Bernoulli distribution. At each t, a random neuron *j* is selected, if U(0, 1)_j <= rate[t] (binoimal sample), spike and select another neuron *j'*, othewise move to the next t.

```{r, echo=FALSE, warning=FALSE, fig.width=6, fig.height=2.5}
qplot(data=mi_exp5[mi_exp5$X %in% c("gain_bp"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line", facets=.~excitability) + theme_bw()  + xlab("Istim") + ylab("MI") + stat_summary(data=mi_exp5[mi_exp5$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

qplot(data=h_exp5[h_exp5$X %in% c("gain_bp"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line", facets=.~excitability) + theme_bw()  + xlab("Istim") + ylab("H") + stat_summary(data=h_exp5[h_exp5$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")

qplot(data=pac_exp5[pac_exp5$X %in% c("gain_bp"),], x=Istim, group=Iosc, color=Iosc, y=mean, geom="line", facets=.~excitability) + theme_bw()  + xlab("Istim") + ylab("PAC") + stat_summary(data=pac_exp5[pac_exp5$X %in% c("stim_p"),], aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
```

* With the right excitability, 
* there is narrow window of stimulus strength in which a multiplicative gain interaction with oscillation improves MI.
* For good MI, H rise above stimulus levels
* H and MI strongly correlated. 

Correlation between PAC and MI?

```{r}
cor.test(mi_exp5[mi_exp5$X %in% c("gain_bp"),]$mean, h_exp5[h_exp5$X %in% c("gain_bp"),]$mean)
cor.test(mi_exp5[mi_exp5$X %in% c("gain_bp"),]$mean, pac_exp5[pac_exp5$X %in% c("gain_bp"),]$mean)
```

## Binary

TODO

# Conclusions

* For mutlipaticative interactions, Poisson models have a much wider range of good PAC than the Synchronous model.
* PAC driven by additive interation in neural (MI) but does increase H.
* PAC driven by subtractive interactions is always bad.
