---
title: "Experiments 71"
author: "Erik J Peterson"
date: "9-1-2015"
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
---


# Exp 71

Are replicates of exp60 except for,

Phase in PAC (OZ) is take from the osc population.

```{r helper_fns, echo=FALSE, fig.width=6, fig.height=4, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(grid)
library(gridExtra)
library(plyr)
library(dplyr)
library(reshape)
library(png)
library(plyr)
library(doParallel)
library(tidyr)
library(ggthemr)
registerDoParallel(cores=10)

path <- "/home/ejp/src/pacological/data"

load.data <- function(path, type, rates, gs, Ns, pns){
  df <- NULL
  for(r_s in rates){
    for(g in gs){
      for(N in Ns){
        for(pn in pns){
          try({
            name <- paste("Istim-", as.character(r_s), 
                          "_g-", as.character(g),
                          "_N-", as.character(N),
                          "_pn-", as.character(pn),
                          "__", as.character(type), 
                          "_summary.csv", sep="")
            di <- read.csv(paste(path, name, sep=""))
            di["Istim"] <- rep(r_s, nrow(di))
            di["g"] <- rep(g, nrow(di))
            di["N"] <- rep(N, nrow(di))
            di["pn"] <- rep(pn, nrow(di))
            
            df <- rbind(df, di)  
          })  
        }
      }
    }
  }
  df
}

load.all.data <- function(path, type, rates, gs, Ns, pns){
  df <- NULL
  for(r_s in rates){
    for(g in gs){
      for(N in Ns){
        for(pn in pns){
          try({
            name <- paste("Istim-", as.character(r_s), 
                          "_g-", as.character(g),
                          "_N-", as.character(N),
                          "_pn-", as.character(pn),
                          "__", as.character(type), 
                          ".csv", sep="")
            di <- read.csv(paste(path, name, sep=""))
            di["Istim"] <- rep(r_s, nrow(di))
            di["g"] <- rep(g, nrow(di))
            di["N"] <- rep(N, nrow(di))
            di["pn"] <- rep(pn, nrow(di))
            
            df <- rbind(df, di)  
          })  
        }
      }
    }
  }
  df
}

load.demo <- function(path, type, rates, ks){
  dexp <- NULL
  for(r_o in rates){
    for(r_s in rates){
      for(k in ks){
        try({
          name <- paste("Iosc-", as.character(r_o), 
                      "_Istim-", as.character(r_s), 
                      "_k", as.character(k), 
                      "_", as.character(type), 
                      ".csv", sep="")
          di <- read.csv(paste(path, name, sep=""))
          di["Iosc"] <- rep(r_o, nrow(di))
          di["Istim"] <- rep(r_s, nrow(di))
          di["k"] <- rep(k, nrow(di))
          
          dexp <- rbind(dexp, di)  
       })
      }
    }
  }
dexp
}


load.demo2 <- function(path, type, rates, gs, Ns, pns){
  df <- NULL
  for(r_s in rates){
    for(g in gs){
      for(N in Ns){
        for(pn in pns){
          try({
            name <- paste("Istim-", as.character(r_s), 
                          "_g-", as.character(g),
                          "_N-", as.character(N),
                          "_pn-", as.character(pn),
                          "__", as.character(type), 
                          ".csv", sep="")
            di <- read.csv(paste(path, name, sep=""))
            di["Istim"] <- rep(r_s, nrow(di))
            di["g"] <- rep(g, nrow(di))
            di["N"] <- rep(N, nrow(di))
            di["pn"] <- rep(pn, nrow(di))
            
            df <- rbind(df, di)  
          })  
        }
      }
    }
  }
  df
}

pprime <- function(r1, r2, v1, v2){
  (r2 - r1) / sqrt((v1 + v2) / 2)
}
```

```{r load71, echo=FALSE, warning=FALSE, message=FALSE}
rates <- c(2, 6, 10, 14, 18, 22, 26, 30)
gs <- c(1,2,3,4,5,6,7,8)
Ns <- c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000)
pns <- c(1)

exp71path <- paste(path, "/exp71/", sep="")
mi_exp71 <- load.data(exp71path, "MI", rates, gs, Ns, pns)
h_exp71 <- load.data(exp71path, "H", rates, gs, Ns, pns)
pac_exp71 <- load.data(exp71path, "PAC", rates, gs, Ns, pns)
```

```{r fig171, fig.width=6, fig.height=4, echo=FALSE, warning=FALSE, message=FALSE}
# -- MI
# Sel N and p
mi_fig71 <- filter(mi_exp71, N == 100, pn == 1.00)

# Get Avg MI for stim
Mstim <- mean((filter(mi_fig71, X == "stim_p"))$mean)
mi_fig71$mean <- mi_fig71$mean - Mstim

# Select, rename, and order 'em
mi_fig71 <- filter(mi_fig71, X %in% c("gain_p", "silenced_p", "summed_p"))
mi_fig71$X <- revalue(mi_fig71$X, c("gain_p"="EI", "summed_p"="E", "silenced_p"="I"))
mi_fig71$X <- factor(mi_fig71$X, levels=c("EI", "E", "I")) 

# Sum and plot
mi_stats <- group_by(mi_fig71, X)
mi_stats <- summarise(mi_stats, M=mean(mean), SD=sd(mean))
limits <- aes(ymax = M + SD, ymin=M - SD)

f71a <- qplot(data=mi_stats, x=X, y=M, geom="bar", stat="identity", width=.75) + geom_errorbar(limits, width=0.2, color="grey") + ylab(expression(paste(Delta, "MI"))) + theme_bw() + geom_hline(yintercept=0, color="grey") + xlab("") + ggtitle("Exp 59") 

# 2B, Series
mi_exp71 %>% 
  filter(N == 100, pn == 1.00, X %in% c("gain_p", "silenced_p", "summed_p", "stim_p")) %>%
  droplevels() -> mi_fig71b

mi_fig71b$X <- revalue(mi_fig71b$X, c("gain_p"="EI", "summed_p"="E", "silenced_p"="I", "stim_p"="S"))

# Get subtract mean I_stim
mi_fig71b %>% select(mean, Istim, g, X) %>% 
  group_by(Istim, g, X) %>%
  cast(Istim + g ~ X, value = "mean") %>%
  mutate(E=E - S, I = I - S, EI = EI - S) %>%
  select(-S) %>% 
  melt(id=c('Istim', 'g'), variable_name = 'model') -> mi_stats

mi_stats$model <- revalue(mi_stats$model, c("EI"="EI"))
mi_stats$model <- factor(mi_stats$model, levels=c("EI", "E", "I"))

f71b <- qplot(data=mi_stats, x=Istim, y=value, facets=.~model, color=g, geom="line", group=g) + 
  theme_bw() + 
  xlim(0,30) + 
  ylab(expression(paste(Delta, "MI"))) +
  geom_hline(yintercept=0, color="grey") + 
  xlab(expression(r[s])) +
  theme(strip.background = element_blank(), axis.title.x = element_text(colour = "red")) +
  ggtitle("Exp 71")
print(f71b)
```

```{r fig271, fig.width=10, fig.height=2, echo=FALSE, warning=FALSE, message=FALSE}
# -- PAC
# -- MI
# Sel N and p
pac_fig71 <- filter(pac_exp71, N == 100, pn == 1.00)

# Select, rename, and order 'em
pac_fig71 <- filter(pac_fig71, X %in% c("gain_p", "silenced_p", "summed_p", "stim_p"))
pac_fig71$X <- revalue(pac_fig71$X, c("gain_p"="EI", "summed_p"="E", "silenced_p"="I", "stim_p"="S"))
pac_fig71$X <- factor(pac_fig71$X, levels=c("S", "EI", "E", "I")) 

# Sum and plot
pac_fig71 %>% group_by(X) %>% summarise(M=mean(mean), SD=sd(mean)) -> pac_stats
limits <- aes(ymax = M + SD, ymin=M - SD)

f71a <- qplot(data=pac_stats, x=X, y=M, geom="bar", stat="identity", width=.75) + 
  geom_errorbar(limits, width=0.2, color="grey") + 
  ylab("SC") + theme_bw() + 
  geom_hline(yintercept=0, color="grey") + 
  xlab("")

# -------
# 3B, Series
pac_exp71 %>% 
  filter(N == 100, pn == 1.00, X %in% c("gain_p", "silenced_p", "summed_p", "stim_p")) %>%
  droplevels()  %>% select(X, mean, std, Istim, g, N, pn) -> pac_fig71b

pac_fig71b$X <- revalue(pac_fig71b$X, c("gain_p"="EI", "summed_p"="E", "silenced_p"="I", "stim_p"="S"))
pac_fig71b$X <- factor(pac_fig71b$X, levels=c("S", "EI", "E", "I"))
f71b0 <- qplot(data=pac_fig71b, x=Istim, y=mean, facets=.~X, color=g, geom="line", group=g) + 
  theme_bw() + 
  xlim(0,30) + 
  ylab("SC") +
  geom_hline(yintercept=0, color="grey") + 
  xlab(expression(r[s])) +
  theme(strip.background = element_blank(), axis.title.x = element_text(colour = "red"))

layoutm <- rbind(
    c(1, 1, 2, 2, 2, 2)
  )
grid.arrange(f71a, f71b0, layout_matrix=layoutm)
```

# Var and rate

## Var

```{r fig.width=16, fig.height=16, echo=FALSE, warning=FALSE, message=FALSE}
exp71path <- paste(path, "/exp71/", sep="")
vars_exp71 <- load.demo2(exp71path, "vars", rates, gs, Ns, pns)
vars_exp71 %>% 
  select(times=X, Istim, g, N, S=stim_p, Ssp=stim_sp, EI=gain_p, I=silenced_p, E=summed_p) -> 
  vars_exp71

mvars <- melt(vars_exp71, id.vars = c("times", "Istim", "g", "N"))


ggplot(data=mvars, aes(x=factor(N), y=value)) + 
  facet_grid(g~variable) + 
  geom_boxplot() + 
  theme_bw() + 
  scale_y_log10() +
  ylab("Var")

ggplot(data=filter(mvars, times < 300, Istim == 14), aes(x=times, y=value, color=variable)) + 
  geom_point() + 
  facet_grid(g~N) + 
  theme_bw() + 
  scale_y_log10()

ggplot(data=filter(mvars, times < 300, g == 4), aes(x=times, y=value, color=variable)) + 
  geom_point() + 
  facet_grid(Istim~N) + 
  theme_bw() + 
  scale_y_log10()
```

## Rates

```{r fig.width=16, fig.height=16, echo=FALSE, warning=FALSE, message=FALSE}
exp71path <- paste(path, "/exp71/", sep="")
poprates_exp71 <- load.demo2(exp71path, "poprates", rates, gs, Ns, pns)
poprates_exp71 %>% 
  select(times=X, Istim, g, N, S=stim_p, Ssp=stim_sp, EI=gain_p, I=silenced_p, E=summed_p) -> 
  poprates_exp71

mpoprates <- melt(poprates_exp71, id.var = c("times", "Istim", "g", "N"))


ggplot(data=mpoprates, aes(x=factor(N), y=value)) + 
  facet_grid(g~variable) + 
  geom_boxplot() + 
  theme_bw() + 
  scale_y_log10() +
  ylab("Rate")

ggplot(data=filter(mpoprates, times < 300, Istim == 14), aes(x=times, y=value, color=variable)) + 
  geom_point() + 
  facet_grid(g~N) + 
  theme_bw() + 
  scale_y_log10()

ggplot(data=filter(mpoprates, times < 300, g == 4), aes(x=times, y=value, color=variable)) + 
  geom_point() + 
  facet_grid(Istim~N) + 
  theme_bw() + 
  scale_y_log10()
```

* Neither `vars` nor `poprates` obviously explain `gain`s MI facilitation.


# Correlate MI/var and MI/rate

```{r fig.width=16, fig.height=16, echo=FALSE, warning=FALSE, message=FALSE}
# Select and name MI
mi_exp71 %>%
  filter(pn == 1) %>%
  select(X, mean, Istim, g, N) %>% 
  cast(Istim + g + N ~ X, value = "mean")  %>% 
  select(Istim, g, N, S=stim_p, EI=gain_p, E=summed_p, I=silenced_p) %>%
  arrange(Istim, g, N) ->
  mi_exp71_stats

# Avg var
vars_exp71 %>% 
  group_by(Istim, g, N) %>% 
  summarise(S=mean(S), EI=mean(EI), E=mean(E), I=mean(I)) %>%
  arrange(Istim, g, N) ->
  vars_exp71_stats

# Avg poprates
poprates_exp71 %>% 
  group_by(Istim, g, N) %>% 
  summarise(S=mean(S), EI=mean(EI), E=mean(E), I=mean(I)) %>%
  arrange(Istim, g, N) ->
  poprates_exp71_stats
```

Correlation between MI and var

```{r}
cor.test(mi_exp71_stats$EI, vars_exp71_stats$EI, method = "spearman")
cor.test(mi_exp71_stats$E, vars_exp71_stats$E, method = "spearman")
cor.test(mi_exp71_stats$I, vars_exp71_stats$I, method = "spearman")
```

Correlation between MI and rates

```{r}
cor.test(mi_exp71_stats$EI, poprates_exp71_stats$EI, method = "spearman")
cor.test(mi_exp71_stats$E, poprates_exp71_stats$E, method = "spearman")
cor.test(mi_exp71_stats$I, poprates_exp71_stats$I, method = "spearman")
```

* `poprate` explains more variance in MI than `var`. 
* All Spearman's are significant (large N). 


## d' and the models

```{r dprime, fig.width=16, fig.height=16, echo=FALSE, warning=FALSE, message=FALSE}
# Converto mean
poprates_exp71 %>%
  group_by(N) %>%
  mutate(S = as.numeric(S) / N[1], 
         Ssp = as.numeric(Ssp) / N[1], 
         EI=as.numeric(EI) / N[1], 
         E=as.numeric(E) / N[1], 
         I=as.numeric(I) / N[1]) -> popmeans_exp71

# Join M and SD
popmeans_exp71$stat <- rep("M", nrow(popmeans_exp71))
vars_exp71$stat <- rep("SD", nrow(vars_exp71))
exp71 <- rbind(popmeans_exp71,vars_exp71)

exp71 %>%
  filter(times < 500) %>%
  ddply(c("times", "Istim", "g", "N"), .parallel=TRUE, .fun=function(df){
    m <- filter(df, stat == "M")
    s_d <- filter(df, stat == "SD")
    EI <- pprime(m[['S']], m[['EI']], s_d[['S']], s_d[['EI']])
    E <- pprime(m[['S']], m[['E']], s_d[['S']], s_d[['E']])
    I <- pprime(m[['S']], m[['I']], s_d[['S']], s_d[['I']])
    ddf <- cbind(EI, E, I)
    ddf[is.nan(ddf)] <- 0
    data.frame(ddf)
  }) -> prime_exp71

prime_exp71 %>%
  gather(pop, dprime, EI, E, I) %>%
  ggplot(aes(x=N, y=dprime, color=pop)) +
#   geom_point() + 
  stat_summary(fun.data = "mean_cl_boot") +
  facet_grid(g~Istim) + 
  theme_bw()

prime_exp71 %>%
  gather(pop, dprime, EI, E, I) %>%
  ggplot(aes(x=Istim, y=dprime, color=g, group=g)) +
#   geom_point() + 
  stat_summary(fun.data = "mean_cl_boot") +
  facet_grid(N~pop) + 
  theme_bw()
```

* `dprime` _does_ track MI (ignoring `N`), but
* `N` doesn't do anything.
* The total MI effect has two parts? Gain as `dprime`, and what ever `N` does?
* `N` does?

```{r fb}
r_s <- 10
r_o <- 2
g <- 2

d_s <- data.frame(S=rpois(1000, r_s))
d_e <- cbind(d_s, data.frame(E=rpois(100, r_s + g * r_o)))
d_i <- cbind(d_s, data.frame(I=rpois(100, r_s - g * r_o)))
d_ei <- cbind(d_s, data.frame(EI=rpois(100, r_s * g * r_o)))

fb1 <- ggplot(data=gather(d_ei, 'pop', x, S, EI), aes(x=x, fill=pop, color=pop)) + 
  geom_density(alpha=0.5, adjust=2) +
  scale_colour_manual(values = c("grey", "black")) + 
  scale_fill_manual(values = c("grey", "black")) + 
  theme_bw() + 
  xlim(0,80) +
  xlab("") +
  ylab("") +
  ggtitle("Gain multiplication increases signal discrimation\nEI") +
  theme(legend.position="none")

fb2 <- ggplot(data=gather(d_e, 'pop', x, S, E), aes(x=x, fill=pop, color=pop)) + 
  geom_density(alpha=0.5, adjust=2) +
  scale_colour_manual(values = c("grey", "black")) + 
  scale_fill_manual(values = c("grey", "black")) + 
  theme_bw() + 
  xlab("") +
  xlim(0,80) +
  ylab("Density (AU)") +
  ggtitle("\nE") +
  theme(legend.position="none")

fb3 <- ggplot(data=gather(d_i, 'pop', x, S, I), aes(x=x, fill=pop, color=pop)) + 
  geom_density(alpha=0.5, adjust=2) +
  scale_colour_manual(values = c("grey", "black")) + 
  scale_fill_manual(values = c("grey", "black")) + 
  theme_bw() + 
  xlab(expression(r)) +
  xlim(0,80) +
  ylab("") +
  ggtitle("\nI") +
  theme(legend.position="none")

fc1 <- prime_exp71 %>%
  gather(pop, dprime, EI, E, I) %>%
  filter(N == 100) %>%
  ggplot(aes(x=Istim, y=dprime, color=g, group=g)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_grid(.~pop) + 
  ylab("d'") +
  geom_hline(yintercept=0, color="grey") +
  theme_bw() + 
  xlab(expression(r[s])) +
  theme(strip.background = element_blank(), axis.title.x = element_text(colour = "red"))

layout <- rbind(
    c(1, 1, 1),
    c(2, 2, 2),
    c(3, 3, 3),
    c(4, 4, 4),
    c(4, 4, 4)
  )
grid.arrange(fb1, fb2, fb3, fc1, layout_matrix=layout)

```
