---
title: "Experiments 30-36"
author: "Erik J Peterson"
date: "June 18, 2015"
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
---

# Binary-type synchrony

```{r helper_fns, echo=FALSE}
load.data <- function(path, type, rates, ks){
  dexp <- NULL
  for(r_o in rates){
    for(r_s in rates){
      for(k in ks){
        try({
          name <- paste("Iosc-", as.character(r_o), 
                      "_Istim-", as.character(r_s), 
                      "_k", as.character(k), 
                      "_", as.character(type), 
                      "_summary.csv", sep="")
          di <- read.csv(paste(path, name, sep=""))
          di["Iosc"] <- rep(r_o, nrow(di))
          di["Istim"] <- rep(r_s, nrow(di))
          di["k"] <- rep(k, nrow(di))
          
          dexp <- rbind(dexp, di)  
       })
      }
    }
  }
dexp
}
```

```{r load, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(gridExtra)

path <- "/home/ejp/src/pacological/data"
rates <- c(5, 30)
ks <- c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30)

exp30path <- paste(path, "/exp30/", sep="")
mi_exp30 <- load.data(exp30path, "MI", rates, ks)
h_exp30 <- load.data(exp30path, "H", rates, ks)
pac_exp30 <- load.data(exp30path, "PAC", rates, ks)

exp31path <- paste(path, "/exp31/", sep="")
mi_exp31 <- load.data(exp31path, "MI", rates, ks)
h_exp31 <- load.data(exp31path, "H", rates, ks)
pac_exp31 <- load.data(exp31path, "PAC", rates, ks)

exp32path <- paste(path, "/exp32/", sep="")
mi_exp32 <- load.data(exp32path, "MI", rates, ks)
h_exp32 <- load.data(exp32path, "H", rates, ks)
pac_exp32 <- load.data(exp32path, "PAC", rates, ks)

exp33path <- paste(path, "/exp33/", sep="")
mi_exp33 <- load.data(exp33path, "MI", rates, ks)
h_exp33 <- load.data(exp33path, "H", rates, ks)
pac_exp33 <- load.data(exp33path, "PAC", rates, ks)

exp34path <- paste(path, "/exp34/", sep="")
mi_exp34 <- load.data(exp34path, "MI", rates, ks)
h_exp34 <- load.data(exp34path, "H", rates, ks)
pac_exp34 <- load.data(exp34path, "PAC", rates, ks)

exp35path <- paste(path, "/exp35/", sep="")
mi_exp35 <- load.data(exp35path, "MI", rates, ks)
h_exp35 <- load.data(exp35path, "H", rates, ks)
pac_exp35 <- load.data(exp35path, "PAC", rates, ks)

exp36path <- paste(path, "/exp36/", sep="")
mi_exp36 <- load.data(exp36path, "MI", rates, ks)
h_exp36 <- load.data(exp36path, "H", rates, ks)
pac_exp36 <- load.data(exp36path, "PAC", rates, ks)
rm(ks, rates)
```

## Exp 30

N = 100

```{r exp30, echo=FALSE, fig.width=10, fig.height=4}
p1 <- qplot(
  data=mi_exp30[mi_exp30$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("MI") + 
  stat_summary(
    data=mi_exp30[mi_exp30$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 30") + 
  facet_grid(Iosc~Istim)

p2 <- qplot(
  data=h_exp30[h_exp30$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("H") + 
  stat_summary(
    data=h_exp30[h_exp30$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 30") + 
  facet_grid(Iosc~Istim)

p3 <- qplot(
  data=pac_exp30[pac_exp30$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("PAC") + 
  stat_summary(
    data=pac_exp30[pac_exp30$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 30") + 
  facet_grid(Iosc~Istim)

grid.arrange(p1, p2, p3, nrow=1)
```

## Exp 32

N = 500

```{r exp32, echo=FALSE, fig.width=10, fig.height=4}
p1 <- qplot(
  data=mi_exp32[mi_exp32$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("MI") + 
  stat_summary(
    data=mi_exp32[mi_exp32$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 32") + 
  facet_grid(Iosc~Istim)

p2 <- qplot(
  data=h_exp32[h_exp32$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("H") + 
  stat_summary(
    data=h_exp32[h_exp32$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 32") + 
  facet_grid(Iosc~Istim)

p3 <- qplot(
  data=pac_exp32[pac_exp32$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("PAC") + 
  stat_summary(
    data=pac_exp32[pac_exp32$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 32") + 
  facet_grid(Iosc~Istim)

grid.arrange(p1, p2, p3, nrow=1)
```

## Exp 34

N = 1000

```{r exp34, echo=FALSE, fig.width=10, fig.height=4}
p1 <- qplot(
  data=mi_exp34[mi_exp34$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("MI") + 
  stat_summary(
    data=mi_exp34[mi_exp34$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 34") + 
  facet_grid(Iosc~Istim)

p2 <- qplot(
  data=h_exp34[h_exp34$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("H") + 
  stat_summary(
    data=h_exp34[h_exp34$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 34") + 
  facet_grid(Iosc~Istim)

p3 <- qplot(
  data=pac_exp34[pac_exp34$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("PAC") + 
  stat_summary(
    data=pac_exp34[pac_exp34$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 34") + 
  facet_grid(Iosc~Istim)

grid.arrange(p1, p2, p3, nrow=1)
```

# Additive and synchronous

```{r exp36, echo=FALSE, fig.width=10, fig.height=4}
p1 <- qplot(
  data=mi_exp36[mi_exp36$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("MI") + 
  stat_summary(
    data=mi_exp36[mi_exp36$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 36") + 
  facet_grid(Iosc~Istim)

p2 <- qplot(
  data=h_exp36[h_exp36$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("H") + 
  stat_summary(
    data=h_exp36[h_exp36$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 36") + 
  facet_grid(Iosc~Istim)

p3 <- qplot(
  data=pac_exp36[pac_exp36$X %in% c("gain_bp"),], 
  x=k, y=mean,
  group=Iosc, 
  geom="line") + 
  theme_bw() + 
  xlim(1,30) + 
  xlab("K") + 
  ylab("PAC") + 
  stat_summary(
    data=pac_exp36[pac_exp36$X %in% c("stim_p"),], 
    aes(x=k, y=mean), 
    geom="line", 
    fun.y=mean, 
    color="red") + 
  ggtitle("Exp 36") + 
  facet_grid(Iosc~Istim)

grid.arrange(p1, p2, p3, nrow=1)
```

# Conclusions

* Little here is as expected....
* MI always worse compared to stimulus
* PAC is weak when oscillation is strong
* PAC often declines as k increases
* As expected from additive rate exps (e.g. exp17-21), no improvement in MI for exp 36.

**Need to rethink the underlying synchrony model and redo in a way that makes sense for the way I'm defining coding and measuring MI/H.**
