---
title: "Experiments 29, 50-2"
author: "Erik J Peterson"
date: "8-12-2015"
output:
  html_document:
    number_sections: yes
    theme: spacelab
    toc: yes
---


# Reparameterization of Exp24, the assembly + noise implementation. 

Here N = 500; Experiments 24-8 were N = 1000. 

Exp 52 was N = 250 (no noise model; a confirmation of past findings)

```{r helper_fns, echo=FALSE, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(gridExtra)

path <- "/home/ejp/src/pacological/data"

load.data <- function(path, type, rates){
  df <- NULL
  for(r_o in rates){
    for(r_s in rates){
      try({
        name <- paste("Iosc-", as.character(r_o), 
                      "_Istim-", as.character(r_s), 
                      "_", as.character(type), 
                      "_summary.csv", sep="")
        di <- read.csv(paste(path, name, sep=""))
        di["Iosc"] <- rep(r_o, nrow(di))
        di["Istim"] <- rep(r_s, nrow(di))
        
        df <- rbind(df, di)  
        })
      }
    }
  df
  }
```

```{r exps, echo=FALSE, warning=FALSE, message=FALSE}
rates <- c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30)

exp29path <- paste(path, "/exp29/", sep="")
mi_exp29 <- load.data(exp29path, "MI", rates)
h_exp29 <- load.data(exp29path, "H", rates)
pac_exp29 <- load.data(exp29path, "PAC", rates)

exp50path <- paste(path, "/exp50/", sep="")
mi_exp50 <- load.data(exp50path, "MI", rates)
h_exp50 <- load.data(exp50path, "H", rates)
pac_exp50 <- load.data(exp50path, "PAC", rates)

exp51path <- paste(path, "/exp51/", sep="")
mi_exp51 <- load.data(exp51path, "MI", rates)
h_exp51 <- load.data(exp51path, "H", rates)
pac_exp51 <- load.data(exp51path, "PAC", rates)

exp52path <- paste(path, "/exp52/", sep="")
mi_exp52 <- load.data(exp52path, "MI", rates)
h_exp52 <- load.data(exp52path, "H", rates)
pac_exp52 <- load.data(exp52path, "PAC", rates)
```

## MIs

### gain

```{r plot_mi_gain, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim29 <- stat_summary(data=subset(mi_exp29, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p29 <- ggplot(data=subset(mi_exp29, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim29 + theme_bw() + ggtitle("exp29\np_n = 0.25") + ylim(0,1)

stim50 <- stat_summary(data=subset(mi_exp50, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p50 <- ggplot(data=subset(mi_exp50, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim50 + theme_bw() + ggtitle("exp50\np_n = 0.5") + ylim(0,1)

stim51 <- stat_summary(data=subset(mi_exp51, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p51 <- ggplot(data=subset(mi_exp51, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim51 + theme_bw() + ggtitle("exp51\np_n = 0.75") + ylim(0,1)

stim52 <- stat_summary(data=subset(mi_exp52, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p52 <- ggplot(data=subset(mi_exp52, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim52 + theme_bw() + ggtitle("exp52\np_n = 1, N = 250") + ylim(0,1)

grid.arrange(p29, p50, p51, p52, nrow=1)
```

* Still divergent from prior gain runs. It seems its not `N` as I thought (from exp 24-7). 
* Exp 51 removed teh background noise and the drive noise. MI effect is back.

### Additive

```{r plot_mi_add, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim29 <- stat_summary(data=subset(mi_exp29, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p29 <- ggplot(data=subset(mi_exp29, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim29 + theme_bw() + ggtitle("exp29\np_n = 0.25") + ylim(0,1)

stim50 <- stat_summary(data=subset(mi_exp50, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p50 <- ggplot(data=subset(mi_exp50, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim50 + theme_bw() + ggtitle("exp50\np_n = 0.5") + ylim(0,1)

stim51 <- stat_summary(data=subset(mi_exp51, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p51 <- ggplot(data=subset(mi_exp51, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim51 + theme_bw() + ggtitle("exp51\np_n = 0.75") + ylim(0,1)

stim52 <- stat_summary(data=subset(mi_exp52, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p52 <- ggplot(data=subset(mi_exp52, X == 'summed_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim52 + theme_bw() + ggtitle("exp52\np_n = 1, N = 250") + ylim(0,1)

grid.arrange(p29, p50, p51, p52, nrow=1)
```

* Always pathological.
* Recruitment doesn't change scaling.


### Subtractive

```{r plot_mi_sub, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim29 <- stat_summary(data=subset(mi_exp29, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p29 <- ggplot(data=subset(mi_exp29, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim29 + theme_bw() + ggtitle("exp29\np_n = 0.25") + ylim(0,1)

stim50 <- stat_summary(data=subset(mi_exp50, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p50 <- ggplot(data=subset(mi_exp50, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim50 + theme_bw() + ggtitle("exp50\np_n = 0.5") + ylim(0,1)

stim51 <- stat_summary(data=subset(mi_exp51, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p51 <- ggplot(data=subset(mi_exp51, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim51 + theme_bw() + ggtitle("exp51\np_n = 0.75") + ylim(0,1)

stim52 <- stat_summary(data=subset(mi_exp52, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p52 <- ggplot(data=subset(mi_exp52, X == 'silenced_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("MI") + stim52 + theme_bw() + ggtitle("exp52\np_n = 1, N = 250") + ylim(0,1)

grid.arrange(p29, p50, p51, p52, nrow=1)
```

* Subtractive interactions (in the prescence of background population noise) leads to beneficial PAC.
* As recruiment (i.e. `n_p`) increases the benefit decreases

- **General note**: even when PAC is beneficial that benefit is sometimes limited to lower values of Istim (multiplicative)
- and is sometimes limited to small values of Iosc (subtractive)
- but not always (multplicative).

- **The benefit of PAC is generally both mechanism dependent and drive dependent.**


## PACs

```{r plot_pac, fig.width=12, fig.height=3, echo=FALSE, warning=FALSE, message=FALSE}
stim29 <- stat_summary(data=subset(pac_exp29, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p29 <- ggplot(data=subset(pac_exp29, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim29 + theme_bw() + ggtitle("exp29\np_n = 0.25") + ylim(0,1)

stim50 <- stat_summary(data=subset(pac_exp50, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p50 <- ggplot(data=subset(pac_exp50, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim50 + theme_bw() + ggtitle("exp50\np_n = 0.5") + ylim(0,1)

stim51 <- stat_summary(data=subset(pac_exp51, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p51 <- ggplot(data=subset(pac_exp51, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim51 + theme_bw() + ggtitle("exp51\np_n = 0.75") + ylim(0,1)

stim52 <- stat_summary(data=subset(pac_exp52, X == 'stim_p'), aes(x=Istim, y=mean), geom="line", fun.y=mean, color="red")
p52 <- ggplot(data=subset(pac_exp52, X == 'gain_p'), aes(x=Istim, y=mean, group=Iosc, color=Iosc)) + geom_line() + ylab("pac") + stim52 + theme_bw() + ggtitle("exp52\np_n = 1, N = 250") + ylim(0,1)

grid.arrange(p29, p50, p51, p52, nrow=1)
```

* If anything, the ability to measure PAC over stimulus is enhanced by the background noise model.
